Regression

### 2018-02-01 paper/R/04_Modelresults.Rmd
new

# 1. The online news market

## Pageviews
```{r}
views1 <- read.csv("../data/alexa/Historical_Traffic_Trends__Pageviews_Percent_1.csv", comment.char="#")
views2 <- read.csv("../data/alexa/Historical_Traffic_Trends__Pageviews_Percent_2.csv", comment.char="#")

views <- left_join(views1, views2 %>% 
                     select(-Metric), by = "Date") %>%
  mutate(date = as.Date(Date, "%m/%d/%Y")) %>%
  select(- c(Metric,Date)) %>%
  gather(key="site", value="views", focus.de:tagesspiegel.de)
```

```{r}
# keeps <- c("spiegel.de", "focus.de", "zeit.de","bild.de",
#           "tagesschau.de")
#drop <- c("stern.de","sueddeutsche.de")

# reach <- reach %>%
#   mutate(date = as.Date(Date, "%m/%d/%Y")) %>%
#   select(- c(Metric,Date)) %>%
#   gather(key="site", value="reach", focus.de:n.tv.de) %>%
#  filter(!site %in% drop)

views <- views %>%
  mutate(site = ifelse(site=="bild.de","Bild.de",site),
       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
       site = ifelse(site=="zdf.de","ZDF.de",site),
       site = ifelse(site=="welt.de","DIE WELT",site),
       site = ifelse(site=="n-tv.de","n-tv.de",site))

```{r}
p1 <- views %>%
  filter(date > as.POSIXct("2017-05-31")) %>%
  ggplot(aes(date, views, color=site)) +
  geom_line(show.legend = F) +
  geom_text_repel(data = views[views$date==max(views$date), ],
                  aes(date, views, label=site),
                  size=2.8, show.legend = F, seed = 1) +
  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-15")),
               breaks = date_breaks("1 month"), 
               labels=date_format("%B %y", tz="CET")) +
  theme(
      #legend.position   = "none",
      legend.text       =  element_text(size=6),
      axis.text.y       = element_text(size = 8)
    ) +
  labs(x="", y="pageviews", color="", title = "", 
      caption = "Source: Alexa Internet, Inc. (www.alexa.com)" )

ggsave(plot= p1,
filename = "../figs/reach.png", device = "png",
width = 6, height = 4,
        dpi = 600
)
```

```{r}
# calculate percentual change
views$perc_change <- (views$views - lag(views$views, n=1)) / (views$views*100)

p1 <- views %>% 
  filter(date >= as.Date("2017-09-17") &
                   date <= as.Date("2017-10-01")) %>%
  ggplot(aes(date, perc_change, color=factor(site))) +
  geom_line(show.legend = F) +
  geom_text_repel(data = views[views$date=="2017-09-24", ],
                  aes(date, perc_change, label=site),
                  size=3, show.legend = F, seed = 5) +
  #scale_color_manual(values = brewer.pal(8,"Dark2")) +
  scale_x_date(breaks = date_breaks("1 day"), labels=date_format("%d.%m.", tz="CET")) +
  labs(x="",y="% change", color="") +
  theme(
      legend.text       =  element_text(size=6),
      axis.text.y       = element_text(size = 8)
    )

ggsave(plot= p1,
filename = "../figs/perc_change.png", device = "png",
width = 6, height = 4,
        dpi = 600
)
```

## Traffic source

```{r}
source1 <- read.csv("../data/alexa/Traffic_Sources_1.csv", 
                    comment.char="#", stringsAsFactors = F)
source2 <- read.csv("../data/alexa/Traffic_Sources_2.csv", 
                    comment.char="#", stringsAsFactors = F)

source <- left_join(source1, source2,
                    by=c("Date","Metric")) %>%
  select(- c(Date)) %>%
  gather(key="site", value="traffic", 
         focus.de:tagesspiegel.de)

source <- source %>%
  mutate(site = ifelse(site=="bild.de","Bild.de",site),
       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
       site = ifelse(site=="zdf.de","ZDF.de",site),
       site = ifelse(site=="welt.de","DIE WELT",site),
       site = ifelse(site=="n-tv.de","n-tv.de",site))

```{r}
p1 <- ggplot(source, aes(site, traffic, fill=Metric,
                   label = round(traffic, digits = 2))) +
  geom_col(alpha = 0.8) +
  geom_text(size = 2, position = position_stack(vjust = 0.5)) +
  labs(x = "", y = "Percentage of total traffic", 
       caption = "Source: Alexa Internet, Inc. (www.alexa.com)") +
  theme(axis.text.x = element_text(angle = 45, size = 8 ))

ggsave(plot= p1,
filename = "../figs/traffic_source.png", device = "png",
width = 6, height = 4,
        dpi = 600
)
```

## Keywords
```{r message=FALSE, warning=FALSE}
setwd("../data/alexa/keywords/")
filenames <- list.files(pattern = ".tsv$")

# create an empty list that will serve as a container to receive the incoming files
list.data<-list()

# create a loop to read in your data
for (i in 1:length(filenames)) {
  list.data[[i]]<-read.delim(filenames[i], comment.char="#")
}

# Create DF
keywords.df <- as.data.frame(list.data[1])

for (i in 2:length(filenames)) {
  keywords.df <- rbind(keywords.df, as.data.frame(list.data[i]))
}
```

```{r}
keepsite <- c("tagesschau.de", "spiegel.de", "zeit.de", 
              "bild.de", "welt.de", "focus.de")

keywords.df.reduced <- keywords.df %>% 
  filter(nchar(as.character(site))>1) %>% filter(site %in% keepsite)
```

```{r}
keywords.df <- keywords.df %>%
  mutate(site = as.character(site)) %>%
  mutate(site = ifelse(site=="bild.de","Bild.de",site),
       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
       site = ifelse(site=="deutschlandfunk.de","DLF",site),
       site = ifelse(site=="zdf.de","ZDF.de",site),
       site = ifelse(site=="welt.de","DIE WELT",site),
       site = ifelse(site=="n-tv.de","n-tv.de",site))
```

### Search Traffic %
```{r}
p1 <- keywords.df %>%
  arrange(desc(Percent_of_traffic)) %>%
  group_by(site) %>%
  top_n(10, Percent_of_traffic) %>%
  ungroup() %>%
  ggplot(aes(reorder(term, Percent_of_traffic), 
             Percent_of_traffic, fill=site)) +
  geom_col(fill=col[1], show.legend = FALSE) +
  theme_bw(base_family = "Roboto", base_size = 7) +
  coord_flip() +
  facet_wrap(~site, scales = "free") +
  labs(x= "", y = "Search traffic %", 
       title = "",
       caption = "Source: Alexa Internet, Inc. (www.alexa.com)")

ggsave(plot= p1,
filename = "../figs/search_traffic.png", device = "png",
width = 9, height = 5,
        dpi = 600
)
```

### Share of voice
```{r}
keyword1 <- c("nachrichten", "news", "bundestagswahl 2017",
            "groko", "jamaika")

keyword2 <- c("cdu","csu","spd","fdp","afd",
           "die linke","die grünen")

```{r}
p1 <- keywords.df %>%
  filter(term %in% keyword1) %>%
  ggplot(aes(site,
             Share_of_voice, fill=term)) +
  geom_col(fill=col[3], show.legend = F) +
  coord_flip() +
  facet_grid(~term, scales = "free") +
  labs(x= "", y = "Share of voice",
       title = ""
       )

ggsave(plot= p1,
filename = "../figs/keywords1.png", device = "png",
width = 6, height = 4,
        dpi = 600
)
```

```{r}
p1 <- keywords.df %>%
  filter(term %in% keyword2) %>%
  ggplot(aes(site,
             Share_of_voice, fill=term)) +
  geom_col(fill=col[3], show.legend = F) +
  coord_flip() +
  facet_grid(~term) +
  labs(x= "", y = "Share of voice",
       caption = "
  Source: Alexa Internet, Inc. (www.alexa.com)
      ",
       title = ""
       )

ggsave(plot= p1,
filename = "../figs/keywords2.png", device = "png",
width = 6, height = 4,
        dpi = 600
)
```

# 2. Data 
```{r caching, echo = FALSE}
load("../output/btw_combined.Rda")
```

## Distribution of articles
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[1], alpha= .8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none"
    )

@@

# 3. Model Results
```{r caching, echo = FALSE}
load("../output/models/STM_stemmed2 40 .Rda")
```

@@

After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
```{r}
sagelabs$cov.betas[[5]]$problabels[,1:10]
```

```{r}
topics <- matrix(c(1, "Great coalition", 2, "Merkel vs. CSU", 3, "Jamaica coalition", 
                   4, "Diesel scandal", 5, "Merkel as chancellor", 6, "Seehover vs. Söder", 
                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "AfD election results", 
                   10, "Steinmeier,Federal President", 11, "IT themes (Data policy, Wifi, Telekom)", 
                   12, "Federal Election in social media", 13, "Climate policy", 14, "G20 Hamburg", 
                   15, "error (text processing failure)", 16, "Education, Pension policy",
                   17, "Reports on individuals", 18, "Family reunion refugees", 19, "Polls federal election", 
                   20, "AfD top candidates Weidel, Storch", 21, "M.Schwesig (SPD)",
                   22, "elections in Niedersachsen", 23, "Court sentences (NSU, Böhmermann vs. Erdogan)", 
                   24, "election capaigns & political talkshows", 25, "German armed forces", 26, "W.Schäuble", 
                   27, "C.Lindner FDP", 28, "Turkey, Russia", 29, "railway problems (DBahn)", 
                   30, "H.Kohl obituary", 31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 
                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
                   37, "AfD in parliament", 38, "Terror attacks (GER)  & police reports", 
                   39, "Church", 40, "RAF"), ncol=2, byrow=T)

@@

### now we can inspect the unclear topics
```{r}
btw %>% filter(topic==17) %>% select(title, gamma, url) %>%
  htmlTable::htmlTable(align="l")
```

## Expected topic proportions

@@

### by newspaper
```{r}
plotNewspaperHistogram <- function(topic){
  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
  tab <- as.data.frame(tab) %>% 
    mutate(site=stmOut$settings$covariates$yvarlevels)

  ggplot(data=tab, aes(x=site, y=tab)) +
    geom_col(fill=col[3]) +
    coord_flip() +
    theme(axis.text = element_text(size=8),
          axis.title = element_text(size=10)) +
    labs(x="", y=paste("expected frequency of topic",topics.df[topic,2], sep=" ")) 
}
```

```{r}
# Topic 1
plotNewspaperHistogram(1)
```

@@

```{r}
freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
freq <- as.data.frame(freq) %>% 
    mutate(site=stmOut$settings$covariates$yvarlevels,
           topic = 1)

for(i in 2:40) {
  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
  freq1 <- as.data.frame(freq1) %>% 
    transmute(site=stmOut$settings$covariates$yvarlevels,
           topic = i,
           freq = freq1)

@@

freq <- freq %>%
  mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
  group_by(topic, ownership) %>%
  summarise(freq_mean = mean(freq)) %>%
  spread(ownership, freq_mean) %>%
  mutate(freq_diff = public - private) %>%
  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
  left_join(., topics.df, by = "topic")
```

@@

### Difference in topic prevalence
The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata). First, users must specify the variable that they wish to use for calculating an effect. If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median. These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.

```{r}
effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
#plot.estimateEffect(effect, "month", topics=c(33), method = "continuous", npoints=500)
```

```{r}
save.image("stm_newsdata.RData")
```

@@

out <- list(call=effect$call, topics=effect$topics, tables=tables)
```

```{r}
coeff <- as.data.frame(do.call(rbind,out$tables))

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("site", "", parameter),
         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic")
```

```{r}
sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")

p1 <- coeff %>% filter(parameter %in% sites) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  coord_flip() +
  facet_wrap(~parameter, ncol = 6) +
  labs(x="", fill="significant at\nthe 5% level") +
  theme(axis.text.x = element_text(angle=90))

@@

ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
dpi = 600)
```

@@

ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
dpi = 600)
```

## Topic Correlation
```{r}
## Create Dataframe with correlations

cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
colnames(cor) <- 1:40

@@

for (i in 2:6) {
  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
  colnames(cor) <- 1:40

@@

```{r}
p1 <- df %>%
  filter(corr>0.1 & corr < 1) %>%
  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
             fill=corr)) +
  geom_tile() +
  facet_wrap(~site, ncol = 6) +
  scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
  labs(x="", y="", fill="correlation") +
  theme_bw(base_family = "Roboto", base_size = 10) +
  theme(axis.text.x = element_text(angle=90, size = 6),
        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

@@

ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
dpi = 600)
```

@@

### Distance metric
Compute different metrices and compare them.

@@

```{r}
stmOut$settings$covariates$yvarlevels[1]
```

```{r}
comb.matrix <- matrix(0, nrow= 36, ncol = 2)

y <- 1
for (i in 1:6) {
  for (j in 1:6) {
    comb.matrix[y,1] <- stmOut$settings$covariates$yvarlevels[i]
    comb.matrix[y,2] <- stmOut$settings$covariates$yvarlevels[j]
    y <- y+1
  }
}
```

```{r}
# Create empty matrix
kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = 40)
names(kld.matrix) <- 1:40
# Populate matrix with JSD Values

x <- 1

for (i in 1:6) {

      print(paste("ylevel = ", i))
    base <- exp(stmOut$beta$logbeta[[i]])
    compare1 <- exp(stmOut$beta$logbeta[[1]])
    compare2 <- exp(stmOut$beta$logbeta[[2]])
    compare3 <- exp(stmOut$beta$logbeta[[3]])
    compare4 <- exp(stmOut$beta$logbeta[[4]])
    compare5 <- exp(stmOut$beta$logbeta[[5]])
    compare6 <- exp(stmOut$beta$logbeta[[6]])

  for (j in 1:40) {

    print(paste("topic = ", j))
    kld.matrix[x,j] <- JSD(base[j,],compare1[j,])
    kld.matrix[x+1,j] <- JSD(base[j,],compare2[j,])
    kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
    kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
    kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
    kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])

  }
    x <- x+6
}

```{r}
## Create DF
kld.df <- as.data.frame(kld.matrix) 
colnames(kld.df) <- 1:40

kld.df <- kld.df %>% mutate(News1 = comb.matrix[,1],
         News2 = comb.matrix[,2]) %>%
  melt(.,id=c("News1","News2"), value.name="JSD",
       variable.name = "topic") %>%
  mutate(topic = as.integer(topic)) %>%
  left_join(., topics.df, by="topic")
```

```{r}
cols <- rev(brewer.pal(11, 'RdYlBu'))

p1 <- kld.df %>%
  filter(!topic %in% c("11","15")) %>%
  filter(News1!=News2) %>%
  ggplot(aes(News2, factor(topic_name), fill = JSD)) + 
  geom_tile() + 
  facet_grid(~News1) + 
  scale_fill_gradientn(colours = cols) +
  labs(x="", y="") +
  theme_bw(base_family = "Roboto", base_size = 11) +
  theme(axis.text.x = element_text(angle=90),
        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

ggsave(plot = p1, filename = "../figs/jsd.png", device = "png",width = 10, height = 8,
dpi = 600)
```

>>>>

# 2. Data 
```{r caching, echo = FALSE}
#load("../output/btw_combined.Rda")
load("../output/btw_comb_ownership.Rda")
```

## Distribution of articles
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(ownership)) +
  geom_bar(fill=col[1], alpha= .8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none"
    )

@@

# 3. Model Results
```{r caching, echo = FALSE}
#load("../output/models/STM_stemmed2 40 .Rda")
load("../output/models/STM_ownership 40 .Rda")
out <- out_ownership
```

@@

After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
```{r}
sagelabs$cov.betas[[1]]$problabels[,1:6]
```

```{r}
topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition",
                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder",
                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "Trends in electoral districts", 
                   10, "Steinmeier, Federal President", 11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
                   12, "Federal Election trends", 13, "Climate policy", 14, "G20 Hamburg", 
                   15, "error (text processing failure)", 16, "Federal budget statistics", 
                   17, "Reports on individuals (Berlin)", 18, "Family reunion refugees", 
                   19, "Polls federal election", 20, "AfD, Weidel in social media", 
                   21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
                   23, "Court sentences, NSU trial", 24, "election capaigns & political talkshows", 
                   25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
                   28, "Turkey, Russia", 29, "railway problems (DBahn)", 30, "H.Kohl obituary", 
                   31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 33, "EU policies", 
                   34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 37, "AfD in parliament", 
                   38, "Terror attacks (GER)  & police reports", 39, "Church", 40, "RAF"), ncol=2, byrow=T)

@@

### now we can inspect the unclear topics
```{r}
btw.2 %>% filter(topic==11) %>% select(title, gamma, url) %>%
  htmlTable::htmlTable(align="l")
```

## 3.1. Topic proportions

@@

### by newspaper
```{r}
# Topic 1
plotNewspaperHistogram(2)
```

@@

```{r}
freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
freq <- as.data.frame(freq) %>% 
    mutate(ownership=stmOut$settings$covariates$yvarlevels,
           topic = 1)

for(i in 2:40) {
  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
  freq1 <- as.data.frame(freq1) %>% 
    transmute(ownership=stmOut$settings$covariates$yvarlevels,
           topic = i,
           freq = freq1)

@@

freq <- freq %>%
  #mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
  group_by(topic, ownership) %>%
  summarise(freq_mean = mean(freq)) %>%
  spread(ownership, freq_mean) %>%
  mutate(freq_diff = public - private) %>%
  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
  left_join(., topics.df, by = "topic")
```

@@

## 3.2. Difference in topic prevalence
The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata). First, users must specify the variable that they wish to use for calculating an effect. If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median. These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.

```{r}
# effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
#                          metadata = out$meta, uncertainty = "None")

effect <- estimateEffect(c(1:40) ~ownership+s(month), stmOut, 
                         metadata = out_ownership$meta, uncertainty = "None")
#save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
```

@@

out1 <- list(call=effect$call, topics=effect$topics, tables=tables)
```

```{r}
coeff <- as.data.frame(do.call(rbind,out1$tables))

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("ownership", "", parameter),
         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic")
```

```{r}
#sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
sites <- c("(Intercept)", "public", "private")
p1 <- coeff %>% filter(parameter %in% sites) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  coord_flip() +
  facet_wrap(~parameter, ncol = 6) +
  labs(x="", fill="significant at\nthe 5% level") +
  theme(axis.text.x = element_text(angle=90))

@@

# ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
# dpi = 600)
```

@@

# ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
# dpi = 600)
```

## 3.3 Topic Correlation
```{r}
## Create Dataframe with correlations
cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
colnames(cor) <- 1:40

@@

for (i in 2:2) {
  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
  colnames(cor) <- 1:40

@@

```{r}
p1 <- df %>%
  filter(corr>0.1 & corr < 1) %>%
  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
             fill=corr)) +
  geom_tile() +
  facet_wrap(~site, ncol = 6) +
  #scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
  labs(x="", y="", fill="correlation") +
  theme_bw(base_family = "Roboto", base_size = 10) +
  theme(axis.text.x = element_text(angle=90, size = 6),
        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

@@

# ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
# dpi = 600)
```

### Network graph
```{r}
i <- 1
cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
cormat <- ifelse(cormat >=0.05, cor, 0)
# 
g <- igraph::simplify(igraph::graph.adjacency(cormat, mode = "undirected", weight=TRUE))
igraph::V(g)$name <- topics.df$topic_name
igraph::V(g)$props <- colMeans(stmOut$theta)

p1 <- topicCorrNetwork(g, stmOut$settings$covariates$yvarlevels[i])
# 
ggsave(
      paste0("../figs/corrplot",i,".png"),
      p1,
      dpi = 300,
      width = 9,
      height = 6
    )
```

@@

## 3.4 Distance metric
Compute different metrices and compare them.

@@

```{r}
k <- stmOut$settings$dim$K
y <- length(stmOut$settings$covariates$yvarlevels)
```

```{r}
## Find all combinations of ylevel
comb.matrix <- matrix(0, 
                      nrow= y^2, 
                      ncol = 2)

z <- 1
for (i in 1:y) {
  for (j in 1:y) {
    comb.matrix[z,1] <- stmOut$settings$covariates$yvarlevels[i]
    comb.matrix[z,2] <- stmOut$settings$covariates$yvarlevels[j]
    z <- z+1
  }
}
```

### Calculate KLD
```{r}
# Create empty matrix
kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
names(kld.matrix) <- 1:k

# Populate matrix with JSD Values
x <- 1
for (i in 1:y) {

    #print(paste("ylevel = ", i))
    base <- exp(stmOut$beta$logbeta[[i]])
    compare1 <- exp(stmOut$beta$logbeta[[1]])
    compare2 <- exp(stmOut$beta$logbeta[[2]])
    # compare3 <- exp(stmOut$beta$logbeta[[3]])
    # compare4 <- exp(stmOut$beta$logbeta[[4]])
    # compare5 <- exp(stmOut$beta$logbeta[[5]])
    # compare6 <- exp(stmOut$beta$logbeta[[6]])

  for (j in 1:k) {

    #print(paste("topic = ", j))
    kld.matrix[x,j] <- KLD(base[j,],compare1[j,])
    kld.matrix[x+1,j] <- KLD(base[j,],compare2[j,])
    # kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
    # kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
    # kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
    # kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])

  }
    x <- x+y
}
```

```{r}
## Create DF
kld.df <- as.data.frame(kld.matrix) 
colnames(kld.df) <- 1:k

kld.df <- kld.df %>% mutate(News1 = comb.matrix[,1],
         News2 = comb.matrix[,2]) %>%
  melt(.,id=c("News1","News2"), value.name="KLD",
       variable.name = "topic") %>%
  mutate(topic = as.integer(topic)) %>%
  left_join(., topics.df, by="topic")
```

### Calculate JSD
```{r}
# Create empty matrix
jsd.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
names(jsd.matrix) <- 1:k

# Populate matrix with JSD Values
x <- 1
for (i in 1:y) {

    #print(paste("ylevel = ", i))
    base <- exp(stmOut$beta$logbeta[[i]])
    compare1 <- exp(stmOut$beta$logbeta[[1]])
    compare2 <- exp(stmOut$beta$logbeta[[2]])
    # compare3 <- exp(stmOut$beta$logbeta[[3]])
    # compare4 <- exp(stmOut$beta$logbeta[[4]])
    # compare5 <- exp(stmOut$beta$logbeta[[5]])
    # compare6 <- exp(stmOut$beta$logbeta[[6]])

  for (j in 1:k) {

    #print(paste("topic = ", j))
    jsd.matrix[x,j] <- JSD(base[j,],compare1[j,])
    jsd.matrix[x+1,j] <- JSD(base[j,],compare2[j,])
    # kld.matrix[x+2,j] <- JSD(base[j,],compare3[j,])
    # kld.matrix[x+3,j] <- JSD(base[j,],compare4[j,])
    # kld.matrix[x+4,j] <- JSD(base[j,],compare5[j,])
    # kld.matrix[x+5,j] <- JSD(base[j,],compare6[j,])

  }
    x <- x+y
}
```

```{r}
## Create DF
jsd.df <- as.data.frame(jsd.matrix) 
colnames(jsd.df) <- 1:k

distance.df <- jsd.df %>% mutate(News1 = comb.matrix[,1],
         News2 = comb.matrix[,2]) %>% 
  melt(.,id=c("News1","News2"), value.name="JSD",
       variable.name = "topic") %>%
  mutate(topic = as.integer(topic)) %>%
  left_join(., kld.df, by=c("News1","News2","topic")) 
```

### Plot 
```{r}
cols <- rev(brewer.pal(11, 'RdYlBu'))

p1 <- distance.df %>%
  filter(!topic %in% c("11","15")) %>%
  filter(News1!=News2) %>%
  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = KLD)) + 
  geom_tile() +
  #facet_wrap(~variable) + 
  scale_fill_gradientn(colours = cols) +
  labs(x="", y="") +
  theme_bw(base_family = "Roboto", base_size = 11) +
  theme(axis.text.y = element_blank(),
        legend.position = "top",
    #axis.text.x = element_text(angle=90),
        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

p2 <- distance.df %>%
  filter(!topic %in% c("11","15")) %>%
  filter(News1!=News2) %>%
  filter(News1=="private") %>%
  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = JSD)) + 
  geom_tile() +
  #facet_wrap(~variable) + 
  scale_fill_gradientn(colours = cols) +
  labs(x="", y="") +
  theme_bw(base_family = "Roboto", base_size = 11) +
  theme(axis.text.x = element_blank(),
        legend.position = "top",
    #axis.text.x = element_text(angle=90),
        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

p2+p1

ggsave(filename = "../figs/distance.png", device = "png",width = 10, height = 8,
dpi = 600)
```
